Respiratory Disease Outbreaks in Toronto Pre, During, and Post Covid-19 Pandemic 

### 2025-05-13 paper/paper.qmd
rough draft of results

format: pdf
number-sections: true
bibliography: references.bib
---

@@

Total & respiratory & Coronavirus:
```{python}
#| label: all-graph
#| fig-cap: "A line plot on a polar axis"

@@

We see that the total number of cases fluctuates with the number of respiratory cases, with number of outbreaks increasing since 2019 to 2022, and beginning to decrease afterwards

The number of cases also fluctuates with the number of respiratory cases and total cases, following the same trend described above.

Composition of Respiratory Illness:
*** insert graph 
```{python}
#| label: composition-chart
#| fig-cap: "A line plot on a polar axis"

@@

Covid / Secondary Disease / Other & Unknown

Influenza:
Number of cases fall from 2019- 2021, with 0 cases in 2021, and increase thereafter.

```{python}
#| label: no-corona-graph
#| fig-cap: "A line plot on a polar axis"

@@

Each has specifics, see general trend of lower number & some w/ slight decrease reported in pre-pandemic & pandemic, with a subsequent increase post.

>>>>

format: 
  pdf: 
    fig-pos: "H"
number-sections: true
bibliography: references.bib
---

@@

## Overall Cases:
```{python}
#| label: all-graph
#| fig-cap: "A line plot on a polar axis"

@@

We see that the total number of cases fluctuates with the number of respiratory cases, with number of outbreaks increasing since 2019 to 2022, and beginning to decrease afterwards.

The number of coronavirus cases also fluctuates with the number of respiratory cases and total cases, following the same trend described above.

## Makeup of Respiratory Outbreaks
```{python}
#| label: composition-chart
#| fig-cap: "Makeup of Respiratory Outbreaks from 2019-2024 inclusive"

@@

It becomes evident that since the end of the pandemic, the proportion of Coronavirus outbreaks compared to non-coronavirus outbreaks has been steadily decreasing.
## Non-Covid Respiratory Outbreaks
```{python}
#| label: no-corona-graph
#| fig-cap: "A line plot on a polar axis"

@@

We see the number of Influenza (A & B), Parainfluenza, Respiratory Syncytial Virus (RSV), Metapneumovirus, and Rhinovirus outbreaks all generally fell to lower levels during the pandemic (2020-2021). 
Post pandemic (2022-2024), all, with the exception of Influenza, have resurged to greater than pre-pandemic (2019) levels. Influenza outbreaks have also increased since the pandemic, but remain at a lower level comparative to 2019.
